### 2022-01-18 paper.tex
task 2

\pagebreak
\section{Task 2 Semantic Decoding}
Semantic decoding translates utterances into the set of sematic concepts (dia\-log acts), which consists of 2 parts: intent (or dialog act type) and sematic slots and values. For instance the sentence "I want to book a flight to Berlin" can be translated into the intent "book" and the slots "flight" and "to" with the value "Berlin"($book(flight, to(Berlin))$).

We can view this as a classification task: having probability for each act type and each slot-value pair.
\begin{center}
    \includegraphics[width=\linewidth]{training-2.png}
\end{center}
Utterances for classification task can be represented as a fixed-size vector with the bag-of-words model. Where we preserve only information about which and how many words are there. To keep the word order information additionally one can use an n-gram model. We can also use delexicalisation to cluster special terms as <area> or <food-type> with the help of ontology in advance. Then several SVMs are trained to classify possible dialog acts (see image below).
\begin{center}
    \includegraphics[width=\linewidth]{semantic-decoding-classification.png}
\end{center}

We also consider several possible utterances (see image).
\begin{center}
    \includegraphics{uncertanty.png}
\end{center}

We can view this as a seq-to-seq task: translating an utterance into a sequence of tags, for ex. "I want to fly from Minsk to Kiev round trip tomorrow" can be translated into the sequence of tags: ["O", "O", "O", "O", "O", "B-fromloc.city\_name", "O", "B-toloc.city\_name", "B-round\_trip", "I-round\_trip", "B-departure\_date"].
\begin{center}
    \includegraphics[width=\linewidth]{training-2-2.png}
\end{center}

In order to do this, we can keep two dictionaries (one for words and one for tags), which will map each word (tag) to a unique integer. We can then use these dictionaries to translate the sequence of words and a sequence of tags into a sequence of integers. Then we can train a model to predict from the sequence of integers a corresponding sequence of tags. This can be a simple RNN with two heads - one for predicting the tags and another for predicting intent. One can also use conditional random fields (CRF) instead.

@@

Macro average can be much lower than a weighted average, because there can be a lot of rare classes with few instances which were not predicted or predicted wrongly while there are not so many classes with a lot of instances, which are therefore predicted correctly.

>>>>

\pagebreak
\section{Semantic Decoding}
Semantic decoding translates user utterances into a set of sematic concepts (dia\-log acts). Dialog act consists of 2 parts: intent (dialog act type) and sematic slots with their values. For instance the sentence "Is there a cheap restaurant in the center?" can be translated into $inform(price=cheap,$ $area$$=center)$. Intent is $inform$, slot $price$ with value $cheap$ and slot $area$ with the value $center$.

We can view semantic decoding as a classification task: having a probabi\-lity for each act type and each slot-value pair.

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{training-2.png}
\end{figure}

Utterances for classification task can be represented as a fixed-size vector, where we preserve only information about which and how many words are there. To keep the word order information additionally one can use an n-gram model. Delexicalisation is used in advance to cluster special terms as $area$ or $food-type$ with the help of ontology. Then several SVMs are trained to classify possible dialog acts (Figure \ref{fig:semantic-decoding-classification}).

\begin{figure}[h!]
    \includegraphics[width=0.998\textwidth]{semantic-decoding-classification.png}
    \label{fig:semantic-decoding-classification}
\end{figure}

Several possible utterances are considered (Figure \ref{several}).
\begin{figure}[h!]
    \centering
    \includegraphics{uncertanty.png}
    \caption{Several Utterances}
    \label{several}
\end{figure}

We can view this as a seq-to-seq task: translating an utterance into a sequence of tags, for ex. "I want to fly from Minsk to Kiev round trip tomorrow" can be translated into the sequence of tags: ["O", "O", "O", "O", "O", "B-fromloc.city\_name", "O", "B-toloc.city\_name", "B-round\_trip", "I-round\_trip", "B-departure\_date"].
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{training-2-2.png}
\end{figure}

Model predicting a sequence of tags can be a simple RNN with two heads - one for predicting the tags and another for predicting intent or conditional random fields (CRF) instead.

@@

Macro average can be much lower than a weighted average (Table \ref{RNNMetrics}), because there can be a lot of rare classes with few instances which were not predicted or predicted wrongly while there are not so many classes with a lot of instances, which are therefore predicted correctly.

\begin{table}
    \centering
    \begin{tabular}{ | c | c | c | c | c |}
        \hline
                        & Precision & Recall & F1-score \\
        \hline
        marco average   & 0.48      & 0.46   & 0.45 \\
        \hline
        weighted average& 0.94      & 0.95   & 0.94 \\
        \hline
    \end{tabular}
    \caption{RNN Metrics}
    \label{RNNMetrics}
\end{table}
